---
title: "codehw3"
format: html
---

GitHub repo: https://github.com/wywydubs/ENVS-193DS_homework-03

```{r set up}
message = FALSE # hide messages
warning = FALSE # hide warning


library(tidyverse) # Load packages
library(here)
library(gt) # chose gt

library(janitor) # Optional packages
library(readxl)
```



# Problem 1 

## A. Data Summarizing

I could compare the average time it took to get out of bed comparing alarm used
versus not used. I would want to know if getting out of bed after a natural 
wake up could be different on average than from an alarm, as there are different
factors like morning obligations hence an alarm versus less grogginess from 
waking up naturally. This comparison could be done by finding the mean of days
with alarm use and the mean of no alarm use, and it could inform me more about
the impact of alarms on my morning routine. 

```{r visualization}
message = FALSE # hide messages
warning = FALSE # hide warning

sleep_log <- read_excel("data/sleep_log.xlsx") #read in data


ggplot(sleep_log, aes(x = `Alarm used?`, # set x and y
                      y = `Time it took to get out of bed (min)`)) +
  geom_jitter(width = 0.2, height = 0, aes(color = `Alarm used?`)) +
  stat_summary(fun = mean, geom = "point", 
               shape = 18, size = 4, color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = 0.2, color = "black") +
  labs(
    title = "Minutes to Get Out of Bed with vs without Alarm",
    x = "Alarm Used?",
    y = "Minutes to Get Out of Bed"
  ) +
  scale_color_manual(values = c("Yes" = "deeppink", "No" = "purple")) +
  theme_minimal()

```













